---
title: "St. Louis County Jail Data"
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r, echo=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(readr)
library(lubridate)
library(purrr)
library(extrafont)
library(scales)
```

```{r}
# Load fonts
font_import()
loadfonts()
```

```{r, echo=FALSE, message=FALSE, warning=TRUE}
files <- list.files("data/clean", pattern = "Bookings", ignore.case = TRUE)

map(files, function(fn) { read_csv(paste("data", "clean", fn, sep = "/")) }) %>%
  bind_rows() -> stl_jail_data
```

After wrangling all of the spreadsheets together, let's ensure that the we have a giant data set, and that the data start at the beginning of 2010 and end at the end of 2017.

```{r, message=FALSE, echo=FALSE, results='hide', warning=TRUE}
dim(stl_jail_data)
head(stl_jail_data)
tail(stl_jail_data)
```

The Date/Time column also has a lot of extra info, and we only need the year. We'll extract the year and add it as a new column. There are also 10 entries whose dates are coded incorrectly, so we need to remove them for any groupings that depend on the date.

```{r, echo=FALSE, results='hide', warning=FALSE}
bookings_with_dates <- stl_jail_data[!is.na(stl_jail_data$BOOKING_DATE_TIME),]
jail_years <- map(bookings_with_dates$BOOKING_DATE_TIME,
                  function(date){
                    year(mdy(strsplit(date, " ")[[1]][[1]]))
                  })

stl_jail_data_with_dates <- bookings_with_dates %>%
  mutate(BOOKING_YEAR = unlist(jail_years)) %>%
  filter(!BOOKING_YEAR %in% c(413, 520, 2729, 431, 2029))       # Filter out 10 wrong dates

write_csv(stl_jail_data_with_dates, "stl_jail_data_with_dates.csv")

# stl_jail_data_with_dates <- read_csv("stl_jail_data_with_dates.csv")
```

## Questions to answer

### Cases by disposition
```{r}
stl_jail_data_with_dates %>% 
  group_by(BOOKING_YEAR, DISPOSITION) %>% 
  summarise(Total_Cases = n()) -> disposition_by_year

disposition_by_year
```

```{r}
bail_dispo_codes <- data.frame(Code = c("PRF", "PRO", "ROR", "TEN", "PTR"), 
                          Dispostion = c("Professional Bond Posted","Property Bond Posted","Recognizance", "10% Bond Posted", "Pretrial Release"))
knitr::kable(bail_dispo_codes)
```

```{r}
stl_jail_data_with_dates %>% 
  group_by(BOOKING_YEAR, DISPOSITION) %>% 
  filter(DISPOSITION %in% bail_dispo_codes$Code) %>% 
  summarise(Total_Cases = n()) %>% 
  ggplot(aes(x = DISPOSITION, y = Total_Cases)) -> gg

gg <- gg + geom_bar(stat = "identity", fill = "#0000ff", width = .8)
gg <- gg + facet_grid(. ~ BOOKING_YEAR)
gg <- gg + xlab("Disposition Code")
gg <- gg + ylab("Total Cases")
gg <- gg + ggtitle("Bookings by bond code, 2010-2017")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5), axis.text.x = element_text(angle = 90))
gg

# ggsave("bookings-by-bond-type.png", plot = gg, device = "png")
```

### Days confined by disposition

```{r}
stl_jail_data_with_dates %>% 
  filter(DAYS_CONFINED > 0) %>% 
  filter(DISPOSITION %in% c("PRF", "PRO", "ROR", "TEN", "CSH")) %>% 
  filter(DISPOSITION != "PTR") %>% 
  group_by(BOOKING_YEAR, DISPOSITION) %>% 
  summarize(Average_Days_Confined = mean(DAYS_CONFINED, na.rm = TRUE)) %>% 
  ggplot(aes(x = reorder(DISPOSITION, Average_Days_Confined) , y = Average_Days_Confined)) -> gg

gg <- gg + geom_bar(stat = "identity", fill = "#0000ff", width = .8)
gg <- gg + facet_grid(. ~ BOOKING_YEAR)
gg <- gg + xlab("Disposition Code")
gg <- gg + ylab("Average Days Confined")
gg <- gg + ggtitle("Average days confined by disposition code (bonds), 2010-2017")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5), axis.text.x = element_text(angle = 90))
gg

# ggsave("days-confined-by-bond-type.png", plot = gg, device = "png")
```

```{r}
stl_jail_data_with_dates %>% 
  filter(DAYS_CONFINED > 0) %>% 
  filter(DISPOSITION %in% c("DSM", "FTP", "NP", "SVT")) %>% 
  filter(DISPOSITION != "PTR") %>% 
  group_by(BOOKING_YEAR, DISPOSITION) %>% 
  summarize(Average_Days_Confined = mean(DAYS_CONFINED, na.rm = TRUE)) %>% 
  ggplot(aes(x = reorder(DISPOSITION, Average_Days_Confined), y = Average_Days_Confined)) -> gg

gg <- gg + geom_bar(stat = "identity", fill = "#0000ff", width = .8)
gg <- gg + facet_grid(. ~ BOOKING_YEAR)
gg <- gg + xlab("Disposition Code")
gg <- gg + ylab("Average Days Confined")
gg <- gg + ggtitle("Average days confined by disposition code (bonds), 2010-2017")
gg <- gg + theme(axis.text.x = element_text(angle = 90))
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5), axis.text.x = element_text(angle = 90))
gg

# ggsave("days-confined-by-dispo-code.png", plot = gg, device = "png")
```

### Total cases per year by disposition code
```{r}
(stl_jail_data_with_dates %>% 
  group_by(BOOKING_YEAR, DISPOSITION) %>% 
  summarise(Total_Cases = n()) -> total_cases_by_dispo_by_year)

write_csv(total_cases_by_dispo_by_year, "total_cases_by_dispo_by_year.csv")
```
## Bookings Per Year By Dispo

```{r}
total_cases_by_dispo_by_year %>% 
  filter(DISPOSITION %in% c("FTP", "DSM", "NP")) %>% 
  ggplot(aes(x = BOOKING_YEAR, y = Total_Cases, col = DISPOSITION)) -> gg

gg <- gg + geom_line()
gg <- gg + theme_minimal()
gg <- gg + scale_color_manual(values = c("#ffd700","#ea5f94","#0000ff"),
                              name = "Disposition",
                              labels = c("Dismissed", "Failure to prosecute", "Nolle prosequi"))
gg <- gg + xlab("Booking year")
gg <- gg + ylab("Total number of bookings")
gg <- gg + ggtitle("Bookings per year by disposition")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg

# ggsave("bookings-DSM-FTP-NP.png", plot = gg, device = "png")
```

```{r}
total_cases_by_dispo_by_year %>% 
  filter(DISPOSITION %in% c("SVT")) %>% 
  ggplot(aes(x = BOOKING_YEAR, y = Total_Cases)) -> gg

gg <- gg + geom_line(color = "#0000ff")
gg <- gg + theme_minimal()
# gg <- gg + scale_color_manual(values = c("#ffd700","#ea5f94","#0000ff"),
#                               name = "Disposition",
#                               labels = c("Dismissed", "Failure to prosecute", "Nolle prosequi"))
gg <- gg + xlab("Booking year")
gg <- gg + ylab("Total number of bookings")
gg <- gg + ggtitle("Bookings resulting in time served dispositions")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg

# ggsave("bookings-time-served.png", plot = gg, device = "png")
```
### Days confined by disposition

```{r}
stl_jail_data_with_dates %>% 
  group_by(BOOKING_YEAR, DISPOSITION) %>%
  summarize(Average_Days_Confined = mean(DAYS_CONFINED, na.rm = TRUE)) -> mean_days_confined_by_dispo

mean_days_confined_by_dispo
```
```{r}
mean_days_confined_by_dispo %>% 
  filter(DISPOSITION == "SVT") %>% 
  ggplot(aes(x = BOOKING_YEAR, y = Average_Days_Confined)) -> gg

gg <- gg + geom_bar(stat = "identity", fill = "#0000ff", width = .3)
gg <- gg + theme_minimal()
gg <- gg + xlab("Booking year")
gg <- gg + ylab("Average days confined")
gg <- gg + ggtitle("Average days confined for cases resulting in time served")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg

# ggsave("aggregate-days-confined-SVT.png", plot = gg, device = "png")
```
```{r}
total_days_confined_by_year <- stl_jail_data_with_dates %>% 
  filter(DISPOSITION == "DSM") %>% 
  group_by(BOOKING_YEAR, IMN) %>% 
  summarise(days_per_imn = (sum(DAYS_CONFINED) / n()))
  
total_days_confined_by_year
```

```{r}
stl_jail_data_with_dates %>% 
  filter(DISPOSITION == "DSM") %>% 
  group_by(BOOKING_YEAR, IMN) %>%
  summarise(days_per_imn = (sum(DAYS_CONFINED) / n())) %>% 
  summarise(Total_Days_Confined = sum(days_per_imn)) %>% 
  ggplot(aes(x = BOOKING_YEAR, y = Total_Days_Confined)) -> gg

gg <- gg + geom_bar(stat = "identity", fill = "#0000ff", width = .3)
gg <- gg + theme_minimal()
gg <- gg + xlab("Booking year")
gg <- gg + ylab("Total days confined")
gg <- gg + ggtitle("Total days confined for cases resulting in dismissals")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg

# ggsave("aggregate-days-confined-DSM.png", plot = gg, device = "png")
```
```{r}
stl_jail_data_with_dates %>% 
  filter(DISPOSITION == "DSM") %>% 
  group_by(BOOKING_YEAR, IMN) %>%
  summarise(days_per_imn = (sum(DAYS_CONFINED) / n())) %>% 
  summarise(Total_Days_Confined = sum(days_per_imn)) %>% 
  hux(add_colnames = TRUE) %>% 
  set_number_format(0)
```

```{r}
stl_jail_data_with_dates %>% 
  filter(DISPOSITION == "NP") %>% 
  group_by(BOOKING_YEAR, IMN) %>% 
  summarise(days_per_imn = (sum(DAYS_CONFINED) / n())) %>% 
  summarise(Total_Days_Confined = sum(days_per_imn)) %>% 
  ggplot(aes(x = BOOKING_YEAR, y = Total_Days_Confined)) -> gg

gg <- gg + geom_bar(stat = "identity", fill = "#0000ff", width = .3)
gg <- gg + theme_minimal()
gg <- gg + xlab("Booking year")
gg <- gg + ylab("Total days confined")
gg <- gg + ggtitle("Total days confined for cases resulting in nolle prosequi dispositions")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg

# ggsave("aggregate-days-confined-NP.png", plot = gg, device = "png")
```
```{r}
stl_jail_data_with_dates %>% 
  filter(DISPOSITION == "FTP") %>% 
  group_by(BOOKING_YEAR, IMN) %>% 
  summarise(days_per_imn = (sum(DAYS_CONFINED) / n())) %>% 
  summarise(Total_Days_Confined = sum(days_per_imn)) %>% 
  ggplot(aes(x = BOOKING_YEAR, y = Total_Days_Confined)) -> gg

gg <- gg + geom_bar(stat = "identity", fill = "#0000ff", width = .3)
gg <- gg + theme_minimal()
gg <- gg + xlab("Booking year")
gg <- gg + ylab("Total days confined")
gg <- gg + ggtitle("Total days confined for cases resulting in failure to prosecute")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg

# ggsave("aggregate-days-confined-FTP.png", plot = gg, device = "png")
```

### Total days confined per year
```{r}
stl_jail_data_with_dates %>%
  group_by(BOOKING_YEAR, IMN) #%>% 
  # distinct(IMN)
  
  #%>% 
  # group_by(BOOKING_YEAR) %>%
  # summarise(Total_Days_Confined = sum(DAYS_CONFINED))
```

```{r}
stl_jail_data_with_dates %>%
  group_by(BOOKING_YEAR, IMN) %>%
  summarise(days_per_imn = (sum(DAYS_CONFINED) / n())) %>% 
  summarise(Total_Days_Confined = sum(days_per_imn)) %>% 
  ggplot(aes(x = BOOKING_YEAR, y = Total_Days_Confined)) -> gg

gg <- gg + geom_bar(stat = "identity", fill = "#0000ff", width = .3)
gg <- gg + scale_y_continuous(labels = comma)
gg <- gg + theme_minimal()
gg <- gg + xlab("Booking year")
gg <- gg + ylab("Aggregate days confined")
gg <- gg + ggtitle("Total days confined per year")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg

# ggsave("aggregate-days-confined.png", plot = gg, device = "png")
```


### Days confined by gender

```{r}
stl_jail_data_with_dates %>% 
  group_by(BOOKING_YEAR, SEX) %>%
  summarize(Average_Days_Confined = mean(DAYS_CONFINED, na.rm = TRUE)) -> mean_days_confined_by_gender

mean_days_confined_by_gender
```
```{r}
mean_days_confined_by_gender %>% 
  ggplot(aes(x = SEX, y = Average_Days_Confined)) -> gg

gg <- gg + geom_bar(stat = "identity", fill = "#0000ff", width = .8)
gg <- gg + facet_grid(. ~ BOOKING_YEAR)
gg <- gg + xlab("Gender")
gg <- gg + ylab("Average Days Confined")
gg <- gg + ggtitle("Average days confined by gender in St. Louis County, 2010-2017")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg 

# ggsave("incarceration-by-gender.png", plot = gg, device = "png")

```
```{r}
stl_jail_data_with_dates %>%
  group_by(BOOKING_YEAR, IMN, SEX) %>% 
  summarise(days_per_imn = (sum(DAYS_CONFINED) / n())) %>%
  group_by(BOOKING_YEAR, SEX) %>% 
  summarise(Total_Days_Confined = sum(days_per_imn))
  # summarise(Total_Days_Confined = sum(days_per_imn)) #%>% 
```

```{r}
stl_jail_data_with_dates %>%
  group_by(BOOKING_YEAR, IMN, SEX) %>% 
  summarise(days_per_imn = (sum(DAYS_CONFINED) / n())) %>%
  group_by(BOOKING_YEAR, SEX) %>% 
  summarise(Total_Days_Confined = sum(days_per_imn)) %>% 
  ggplot(aes(x = SEX, y = Total_Days_Confined)) -> gg

gg <- gg + geom_bar(stat = "identity", fill = "#0000ff", width = .8)
gg <- gg + facet_grid(. ~ BOOKING_YEAR)
gg <- gg + scale_y_continuous(labels = comma)
gg <- gg + xlab("Gender")
gg <- gg + ylab("Total Days Confined")
gg <- gg + ggtitle("Aggregate days confined in St. Louis County by gender, 2010-2017")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg 

# ggsave("aggregte-incarceration-by-gender.png", plot = gg, device = "png")

```
```{r}
stl_jail_data_with_dates %>% 
  filter(OFFENSE_TYPE == "M") %>% 
  group_by(BOOKING_YEAR, IMN) %>%
  summarise(days_per_imn = (sum(DAYS_CONFINED) / n())) %>%
  summarise(Total_Days_Confined = sum(days_per_imn)) %>% 
  # summarise(Total_Days_Confined = sum(DAYS_CONFINED)) %>% 
  ggplot(aes(x = BOOKING_YEAR, y = Total_Days_Confined)) -> gg

gg <- gg + geom_bar(stat = "identity", fill = "#0000ff", width = .3)
gg <- gg + scale_y_continuous(labels = comma)
gg <- gg + theme_minimal()
gg <- gg + xlab("Booking year")
gg <- gg + ylab("Aggregate days confined")
gg <- gg + ggtitle("Total days confined per year for misdemeanor cases")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg 

# ggsave("total-misdemeanor-days-confined.png", plot = gg, device = "png")
```

```{r}
mean_days_confined_by_gender %>%
  filter(SEX == "F") %>% 
  ggplot(aes(x = BOOKING_YEAR, y = Average_Days_Confined)) -> gg

gg <- gg + geom_line(color = "#0000FF")
gg <- gg + theme_minimal()
gg <- gg + xlab("Year")
gg <- gg + ylab("Average Days Confined")
gg <- gg + ggtitle("Average length of confinement for women in St. Louis County, 2010-2017")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg

# ggsave("average-length-of-confinement-for-women.png", plot = gg, device = "png")
```

```{r}
stl_jail_data_with_dates %>% 
  filter(DAYS_CONFINED > 0) %>%
  group_by(BOOKING_YEAR, SEX) %>%
  summarise(Total_Confined = n()) -> total_confined_by_gender_by_year

total_confined_by_gender_by_year
```

```{r}
total_confined_by_gender_by_year %>% 
    ggplot(aes(x = SEX, y = Total_Confined)) -> gg

gg <- gg + geom_bar(stat = "identity", fill = "#0000FF", width = .8)
gg <- gg + facet_grid(. ~ BOOKING_YEAR)
gg <- gg + xlab("Gender")
gg <- gg + ylab("Total number of bookings resulting in confinement")
gg <- gg + ggtitle("Bookings resulting in confinement by gender, 2010-2017")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg

# ggsave("bookings-resulting-in-confinement-by-gender-barplot.png", plot = gg, device = "png")
```

```{r}
total_confined_by_gender_by_year %>%
    filter(SEX == "F") %>%
    ggplot(aes(x = BOOKING_YEAR, y = Total_Confined)) -> gg

gg <- gg + geom_line(color = "#0000FF")
gg <- gg + theme_minimal()
gg <- gg + xlab("Gender")
gg <- gg + ylab("Total number of bookings resulting in confinement (females only)")
gg <- gg + ggtitle("Bookings resulting in confinement (females only), 2010-2017")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg

# ggsave("bookings-resulting-in-confinement-for-women.png", plot = gg, device = "png")
```
```{r}
total_confined_by_gender_by_year %>%
    ggplot(aes(x = BOOKING_YEAR, y = Total_Confined, color = SEX)) -> gg

gg <- gg + geom_line()
gg <- gg + theme_minimal()
gg <- gg + xlab("Gender")
gg <- gg + ylab("Total number of bookings resulting in confinement")
gg <- gg + ggtitle("Bookings resulting in confinement in St. Louis County, 2010-2017")
gg <- gg + scale_color_manual(values = c("#ffd700","#ea5f94"),
                              name = "Gender",
                              labels = c("F", "M"))
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg

# ggsave("bookings-resulting-in-confinement-by-gender.png", plot = gg, device = "png")
```


### Average number of days confined per offense type, per year.

We're interested in seeing the average days confined by year and offense type.

```{r, echo=FALSE}
stl_jail_data_with_dates %>%
  filter(OFFENSE_TYPE != "D") %>% 
  group_by(BOOKING_YEAR, OFFENSE_TYPE) %>%
  summarise(Average_Days_Confined = mean(DAYS_CONFINED, na.rm = TRUE), Max_Days_Confined = max(DAYS_CONFINED), Median_Days_Confined = median(DAYS_CONFINED), Count = n()) -> summary_by_year_offense

summary_by_year_offense
```

What does that look like visually?
```{r, echo=FALSE}
summary_by_year_offense %>% 
  filter(BOOKING_YEAR != 2014 & OFFENSE_TYPE != "U") %>%            # Filter out one outlier in 2014
  ggplot(aes(x = reorder(OFFENSE_TYPE, Average_Days_Confined), y = Average_Days_Confined)) -> gg

gg <- gg + geom_bar(stat = "identity", fill = "#0000FF", width = .8)
gg <- gg + facet_grid(. ~ BOOKING_YEAR)
gg <- gg + xlab("Offense Type")
gg <- gg + ylab("Average Days Confined")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg

ggsave("average-days-confined-by-offense-type.png", plot = gg, device = "png")
```

In order to get these bar charts, we had to remove one extreme outlier in the 2014 data. In the interests of completeness, this is that outlier:

```{r, echo=FALSE}
stl_jail_data_with_dates %>% filter(BOOKING_YEAR == 2014 & DAYS_CONFINED == 491 & ARREST_AGENCY == "JUSTICE SERVICES") %>% arrange(desc(OFFENSE_TYPE))
```

### Comparison of municipal bonds and criminal court bonds

(Need to figure out which fields and which values are municipal/criminal for this one. It can't be as simple as the ones that do/don't have the word municipal in the name, can it?)
```{r, echo=FALSE}
# stl_jail_data_with_dates %>% 
#   filter()
```


### Total cases per court by year

```{r, echo=FALSE}
stl_jail_data_with_dates %>% 
  group_by(BOOKING_YEAR, COURT_NAME) %>% 
  summarise(Count = n()) %>%
  arrange(BOOKING_YEAR, desc(Count))
```

### Total cases per arresting agency by year

```{r, echo=FALSE}
stl_jail_data_with_dates %>% 
  group_by(BOOKING_YEAR, ARREST_AGENCY) %>% 
  summarise(Count = n()) %>%
  arrange(BOOKING_YEAR, desc(Count))
```

### Total cases by charge per year

```{r, echo=FALSE}
stl_jail_data_with_dates %>% 
  group_by(BOOKING_YEAR, CHARGE_DESCRIPTION) %>% 
  summarise(Count = n()) %>%
  arrange(BOOKING_YEAR, desc(Count))
```

### Total cases by bond code per year

```{r, echo=FALSE}
stl_jail_data_with_dates %>% 
  group_by(BOOKING_YEAR, BOND_CODE) %>% 
  filter(BOND_CODE != "NA") %>% 
  summarise(Count = n()) %>%
  arrange(BOOKING_YEAR, desc(Count)) -> bond_code_by_booking_year

bond_code_by_booking_year
```

```{r, echo=FALSE}

bond_code_by_booking_year %>% 
  ggplot(aes(x = reorder(BOND_CODE, Count), y = Count)) -> gg

gg <- gg + geom_bar(stat = "identity", fill = "#0000FF", width = .8)
gg <- gg + facet_grid(. ~ BOOKING_YEAR)
gg <- gg + xlab("Bond code")
gg <- gg + ylab("Total number of cases")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))

gg

# ggsave("total-cases-by-bond-code.png", plot = gg, device = "png")
```

### Average days confined by year

```{r, echo=FALSE}
stl_jail_data_with_dates %>% 
  group_by(BOOKING_YEAR) %>% 
  summarise(Average_Days_Confined = mean(DAYS_CONFINED), 
            Max_Days_Confined = max(DAYS_CONFINED),
            Median_Days_Confined = median(DAYS_CONFINED)) %>%
  arrange(BOOKING_YEAR)
```


### Average days confined by offense

```{r, echo=FALSE}
stl_jail_data_with_dates %>% 
  group_by(CHARGE_DESCRIPTION) %>% 
  summarise(Average_Days_Confined = mean(DAYS_CONFINED), 
            Max_Days_Confined = max(DAYS_CONFINED),
            Median_Days_Confined = median(DAYS_CONFINED)) %>% 
  arrange(desc(Average_Days_Confined))
```

### Total cases by offense type per year

```{r, echo=FALSE}
stl_jail_data_with_dates %>% 
  filter(OFFENSE_TYPE != "D") %>% 
  group_by(BOOKING_YEAR, OFFENSE_TYPE) %>% 
  summarise(Count = n()) %>%
  arrange(BOOKING_YEAR, desc(Count)) -> offense_type_by_year

offense_type_by_year
```

```{r, echo=FALSE}

offense_type_by_year %>% 
  ggplot(aes(x = reorder(OFFENSE_TYPE, Count), y = Count)) -> gg

gg <- gg + geom_bar(stat = "identity", fill = "#0000FF", width = .8)
gg <- gg + facet_wrap(~ BOOKING_YEAR) 
gg <- gg + xlab("Offense type")
gg <- gg + ylab("Total number of cases")
gg <- gg + ggtitle("Total cases by offense type, 2010-2017")
gg <- gg + theme(text = element_text(family = "Fira Sans Light", size = 12, hjust = .5))
gg

# ggsave("total-cases-by-offense-type.png", plot = gg, device = "png")
```




